---
title: "Homework 1"
author: "danfeis"
date: "2019/4/30"
output: html_document
---

```{r include=FALSE}
setwd("E:/KU bioinformatics/block 4/high throughout/week1/data")
```

## Question 1
```{r message=FALSE}
library("babynames")
library("tidyverse")
#Hey
```

### 1a
```{r}
P.name<-head(babynames %>% select(sex,name,n,prop) %>% filter(str_detect(name,"^P") & sex=="F")%>%group_by(name)%>%summarise(name_sum=sum(n))%>%arrange(desc(name_sum)),5)
P.name
```

### 1b
```{r}
p.nameyear<-babynames%>%filter(name=="Patricia"|name=="Pamela"|name=="Phyllis"|name=="Peggy"|name=="Paula")%>%filter(sex=="F")%>%arrange(desc(n))
p.nameyear
ggplot(data=p.nameyear,mapping=aes(x=year,y=n))+geom_line()+facet_wrap(~name)
ggplot(data=p.nameyear,mapping=aes(x=year,y=prop))+geom_line()+facet_wrap(~name)
```

## Question 2
In the same dataset, is the name Arwen significantly more (or less) common in 2004 vs 1990? Is the change significant? What is the likely cause? 
```{r}
Arwen<-babynames%>%filter(year==2004 | year==1990)%>%filter(name=="Arwen")%>%select(year,name,n)
nonArwen<-babynames%>%filter(year==2004 | year==1990)%>%filter(name!="Arwen")%>%group_by(year)%>%summarise(n=sum(n))%>%mutate(name="nonArwen")
Arwen_bind<-bind_rows(Arwen,nonArwen)%>%spread(year,n)
Arwen_bind
fisher.test(as.matrix(Arwen_bind[2:3]))
```

It is due to release of a movie: the lord of rings

## Question 3
```{r}
flowers<-read_tsv("E:/KU bioinformatics/block 4/high throughout/week1/data/flowers.txt")
Sepal<-flowers%>%select(Sepal.Length,Sepal.Width,Species)%>%mutate(type="Sepal")%>%rename(length=Sepal.Length,width=Sepal.Width)
Sepal
Petal<-flowers%>%select(Petal.Length,Petal.Width,Species)%>%mutate(type="Petal")%>%rename(length=Petal.Length,width=Petal.Width)
Petal
bind<-bind_rows(Petal,Sepal)
bind
```

```{r}
ggplot(data=bind,mapping=aes(x=length,y=width,color=Species))+geom_point()+geom_smooth(method = "lm",fullrange=TRUE)+facet_wrap(~type,scales = "free")
```

## Question 4
```{r}
chip<-read_tsv("E:/KU bioinformatics/block 4/high throughout/Group work1/hw1_final/chip_mm5.txt")
chip
```

### hypothesis 1
H0: Binding scores are dependent on chromosome
H1: Binding scores are independent on chromosome
```{r}
ggplot(data=chip,mapping=aes(x=score))+geom_density()+facet_wrap(~chr,scales = "free")
```

```{r}
chip.mean<-chip%>%group_by(chr)%>%summarise(chr.mean=mean(na.omit(score)))
chip.mean
ggplot(data=chip.mean,mapping=aes(x=as.factor(chr),y=chr.mean))+geom_bar(stat = "identity")
```

```{r}
ggplot(data=chip,mapping=aes(x=as.factor(chr),y=score,fill=as.factor(chr)))+geom_boxplot()
```

```{r}
oneway.test(score~as.factor(chr),data=chip)
pairwise.t.test(chip$score,g=as.factor(chip$chr))
```

### hypothesis 2
H0: Binding site widths (end-start) are dependent on chromosome
h1: Binding site widths (end-start) are independent on chromosome
```{r}
ggplot(data=chip,mapping=aes(x=chr,y=end-start,fill=as.factor(chr)))+geom_boxplot()
```

```{r}
width.mean<-chip%>%group_by(chr)%>%summarise(width.mean=mean(na.omit(end-start)))
width.mean
ggplot(data=width.mean,mapping=aes(x=as.factor(chr),y=width.mean))+geom_bar(stat = "identity")
```

```{r}
ggplot(data=chip,mapping=aes(x=end-start))+geom_density()+facet_wrap(~chr)
```

```{r}
kruskal.test(end~as.factor(chr), data=chip)
pairwise.wilcox.test(chip$score,g=as.factor(chip$chr))
```

